Coming to Germany: Pre-migration language skills, Job search and Labor market outcomes

### 2018-08-31 Paper 2.tex
Update Paper 2.tex

This is an important research question because by understanding thoroughly the mechanisms through which language skills at arrival exert an influence on later labor market outcomes, policy makers can make informed decisions to improve immigrants' integration immediately after they arrive to the host countries. Therefore, this paper attempts to explore the role of the pre-migration language skills on the current labor market outcomes of immigrants in Germany. More importantly, this aims to open the black-box to disentangle \textit{how} and \textit{why} language proficiency exerts its influence on labor market success of immigrants.

In light of existing literature, which finds mostly positive effects of contemporaneous language skills on wages, it is important to distinguish between pre--migration language skills and current language skills which have been already influenced by labor market experience in host countries. Because from the methodological point of view, measuring the effects of current language skills on wages could result in a spurious regression due to reverse causality (xxx). To avoid this problem, on the one hand, language skills should ideally be measured before the labor market outcomes, for instance, it is better to use pre--migration than current language skills. But on the other hand, there has been no empirical evidence why pre--migration language skills should have an effect on current labor market outcomes.

@@

@@

\subsection{The job search behavior of immigrants}

The point of departure in previous literature is the contemporaneous language skills, therefore, they do not discuss the job search behaviors of immigrants. But as a most important and visible human capital component in the migration history, language skills, in particular, pre--migration language skills obviously have an impact on the choice of job search methods.

>>>>

This is an important research question because by understanding thoroughly the mechanisms through which language skills at arrival exert an influence on later labor market outcomes, policy makers can make informed decisions to improve immigrants' integration immediately after they arrive in the host countries. This paper attempts to explore the role of the pre-migration language skills on the current labor market outcomes of immigrants in Germany. More importantly, this aims to open the black-box to disentangle \textit{how} and \textit{why} language proficiency exerts its influence on labor market success of immigrants.

In light of existing literature, which finds mostly positive effects of contemporaneous language skills on wages, it is important to distinguish between pre--migration language skills and current language skills which have been already influenced by labor market experience in host countries. From the methodological point of view, measuring the effects of current language skills on wages could result in a spurious regression due to reverse causality (xxx). To avoid this problem, on the one hand, language skills should ideally be measured before the labor market outcomes, for instance, it is better to use pre--migration than current language skills. But on the other hand, there has been no empirical evidence why pre--migration language skills should have an effect on current labor market outcomes.

@@

I also extend the analysis in two directions. First, I analyse the heterogeneous effects for different groups of immigrants, and find out that only the group of labor migrants as opposed to the group of family and humanitarian migrants actually drive the results found earlier. Second, I use the direct measure of network quality proposed by Cappellari and Tatsiramos (2015), namely, number of employed friends and number of educated friends within the closest ties to explain why using social networks might not necessarily be an effective choice of job search for a decent job.

@@

\subsection{The job search behavior of immigrants}
Like natives, immigrants also use a variety of methods to seek for jobs. These methods include the use of public and private employment agencies, responding to job advertisements on public media (newspapers or the Internet), or relying on their network of family and friends (Battu et al., 2011). The point of departure in previous literature is the contemporaneous language skills, therefore, they do not discuss the job search behaviors of immigrants. But as a most important and visible human capital component in the migration history, language skills, in particular, pre--migration language skills obviously have an impact on the choice of job search methods. And these job search methods, in turn, do matter in subsequent labor market outcomes (Battu et al., 2011).
